Don't Mind the Gap: Bridging Network-wide Objectives and Device-level Configurations

### 2016-06-21 paper/v2/paper-edited.tex
adding changes for Todd's comments

%\para{Syntax}
The \sysname FE is just a thin layer atop the RIR for describing preference-based path constraints.
Figure~\ref{fig:rir-syntax} shows the RIR syntax. A policy has one or more constraints, each of which has a test on the type of route and a corresponding set of preferred regular paths. Regular paths are regular expressions where the base characters are abstract locations---either a router or an AS. Special \In{} and \Out{} symbols refer to any internal or external location respectively. In addition, $\Sigma$ refers to any symbol. We also use the standard regular expression abbreviation $r^+$ for $r \cdot r^*$, a sequence of one or more occurrences of $r$. Predicates ($t$) consist of logical boolean connectives (and, or, not) as well as tests that match a particular prefix (or group of prefixes) and tests for route advertisments with a particular community value (i.e., an integer value associated with a path).
%% For example, the constraint
%% \[(\textit{prefix}=74.3.28.0/24) \Link \\
%% (as200 \cdot \In^+) \Prefer (as100 \cdot \In^+)
%% \]
%% describes a more-preferred set of paths for traffic announced by a prefix no less specific than \CD{74.125.28.0/24}, which starts at AS 200, before entering and staying inside the user's network to get to the destination, and a less-preferred set of paths that start at AS 100 and are otherwise the same. The plus operator $\In^+$ stands for $\In \cdot \In^*$, at least one internal hop. Tests over route types use standard boolean connectives, and can refer to both prefixes and route community values.

@@

%
We say that a PGIR node $x_1$ is a \emph{shadow} of topology location $x$ when $x_1 \in V'$ and $loc(x_1) = x$. As a shorthand, we write $x_1 \approx x_2$ when $x_1$ and $x_2$ are both shadows for the same topology location.
%
%Throughout the remainder of the paper, we will use metavariables without subscripts such as $x$ to represent topology locations, and we will use similar metavariables with subscripts such as $x_1$ or $x_2$ to represent shadows of $x$ (i.e., PGIR nodes for location $x$).

@@

To demonstrate the difficulty of generating device-local preferences, consider the simple policy for the topology in Figure~\ref{fig:unimplementable}, which says to prefer the top path over the bottom path:
%
$(\CD{A} \cdot \CD{B} \cdot \CD{D} \cdot \CD{E} \cdot \CD{G})  \Prefer (\CD{A} \cdot \CD{C} \cdot \CD{D} \cdot \CD{F} \cdot \CD{G})$.
%
How could such a policy be implemented in BGP? Suppose we set the local preferences to have $D$ prefer $E$ over $F$, and have $A$ prefer $B$ over $C$. This works as expected under normal conditions, however, if the B--D link fails, then suddenly $D$ has made the wrong decision by preferring $E$. Traffic will now follow the
$A \cdot C \cdot D \cdot E \cdot G$ path, even though this path was not allowed by the policy. This is a violation of \emph{soundness}: The distributed implementation has used a route not specified by the policy. To make matters worse, the second preference $A \cdot C \cdot D \cdot F \cdot G$ is available in the network but not being used. This is a violation of \emph{completeness}: A path for the best possible route available exists in the network but is not being used by the distributed implementation.
%
The soundness violation could be fixed by tagging and filtering route advertisements appropriately so that $C$ rejects routes that go through $E$, however the completeness violation cannot be fixed. In fact, this policy cannot be implemented in BGP in a way that is policy compliant under all failures.

@@

The problem of determining local preferences for each router is closely reflected in the structure of the PGIR. In particular, whenever a given router appears in multiple different contexts in the PGIR (i.e., as multiple PGIR nodes that are shadows of the router), then the compiler must decide which shadow to prefer.
%
In our compilation example from Figure~\ref{fig:example-compilation}, the topology node $C$ can receive an advertisement from $E$ in shadow $(C,-,2)$ or it can receive an advertisement from its neighbor $D$ in shadow $(C,3,2)$.
%
The compiler's task is to determine a \emph{total ordering} of shadow nodes for each router in the topology, which reflects the relative preference of advertisements received in each shadow. For example, if the compiler determines that, for router $C$, shadow $(C,3,2)$ can be locally preferred to shadow $(C,-,2)$, written as $(C,3,2) \leq_{lp} (C,-,2)$, then this means that $C$ will prefer advertisements heard from $D$ (with tag $(2,2)$) over $E$ (with tag $(-,2)$). Section~\ref{sec:abgp} discusses our encoding of preferences and filters in more detail.

@@

As shown in \S\ref{sec:motivation}, BGP aggregation can lead to subtle black-holing of traffic when failures occur. Deciding when this can happen requires knowledge of the routing policy and not just the topology. For instance, a policy might require all traffic for a particular prefix to go over a single link before being aggregated, even if there are several available in the toplogy. If that link fails, a black hole might be introduced.
%
Because the PGIR encodes the complete user policy and topology,  \sysname can efficiently check that aggregates do not black hole traffic for up to $k$ failures.

We frame the aggregation problem as a problem of connectivity in the PGIR. Specifically, for each prefix that falls under an aggregate, we find a lower bound on the number of failures required to disconnect the prefix origin from its aggregation point. The difficulty is that the same links in the topology can appear in multiple places in the PGIR.
%

We adopt the following simple strategy to find a lower bound on
the number of failures: $i)$ pick a random start-to-end path in the PGIR, $ii)$ remove all edges in the PGIR for the set of topological edges chosen, and $iii)$ repeat until no such path exists.
The number of PGIR paths that we are able to remove is a lower bound on the number of failures required to disconnect the prefix from its aggregate.

For example, recall the datacenter example from \S\ref{sec:motivation}, with the policy
\CD{PG1} \Path \text{ }\End(\CD{A}), where \CD{PG1} falls under the \CD{PG} aggregate. Figure~\ref{fig:aggregation-safety} shows the simplified PGIR. Since the compiler knows aggregation will occur at $X$, and it knows that the \CD{PG1} prefix will originate at $A$, we can compute the number of failures it would take to disconnect $A$ from $X$. We could remove the $A$--$D$--$X$ path first. We would then need to remove any other $A$--$D$ or $D$--$X$ links from the PGIR (in this case none). Next, we could remove the links along the $A$--$C$--$X$ path, repeating the process. Because $A$ is then disconnected from $X$, the compiler knowns that 2 is a lower bound on the number of failures for aggregation safety for prefix \CD{PG1}. This process is repeated for other aggregation locations (e.g., $Y$).

@@

\section*{Acknowledgement}

>>>>

%\para{Syntax}
The \sysname FE is just a thin layer atop the RIR for describing preference-based path constraints.
Figure~\ref{fig:rir-syntax} shows the RIR syntax. A policy has one or more constraints, each of which has a test on the type of route and a corresponding set of preferred regular paths. Regular paths are regular expressions where the base characters are AS numbers representing either a router or an external AS. Special \In{} and \Out{} symbols refer to any internal or external location respectively. In addition, $\Sigma$ refers to any symbol. We also use the standard regular expression abbreviation $r^+$ for $r \cdot r^*$, a sequence of one or more occurrences of $r$. Predicates ($t$) consist of logical boolean connectives (and, or, not) as well as tests that match a particular prefix (or group of prefixes) and tests for route advertisments with a particular community value (i.e., an integer value associated with a path).
%% For example, the constraint
%% \[(\textit{prefix}=74.3.28.0/24) \Link \\
%% (as200 \cdot \In^+) \Prefer (as100 \cdot \In^+)
%% \]
%% describes a more-preferred set of paths for traffic announced by a prefix no less specific than \CD{74.125.28.0/24}, which starts at AS 200, before entering and staying inside the user's network to get to the destination, and a less-preferred set of paths that start at AS 100 and are otherwise the same. The plus operator $\In^+$ stands for $\In \cdot \In^*$, at least one internal hop. Tests over route types use standard boolean connectives, and can refer to both prefixes and route community values.

@@

%
We say that a PGIR node $x_1$ is a \emph{shadow} of topology location $x$ when $x_1 \in V'$ and $loc(x_1) = x$. As a shorthand, we write $x_1 \approx x_2$ when $x_1$ and $x_2$ are both shadows of the same topology location (i.e., $loc(x_1) = loc(x_2)$).
%
%Throughout the remainder of the paper, we will use metavariables without subscripts such as $x$ to represent topology locations, and we will use similar metavariables with subscripts such as $x_1$ or $x_2$ to represent shadows of $x$ (i.e., PGIR nodes for location $x$).

@@

To demonstrate the difficulty of generating device-local preferences, consider the simple policy for the topology in Figure~\ref{fig:unimplementable}, which says to prefer the top path over the bottom path:
%
$(\CD{A} \cdot \CD{B} \cdot \CD{D} \cdot \CD{E} \cdot \CD{G})  \Prefer (\CD{A} \cdot \CD{C} \cdot \CD{D} \cdot \CD{F} \cdot \CD{G})$.
%
How could such a policy be implemented in BGP? Suppose we set the local preferences to have $D$ prefer $E$ over $F$, and have $A$ prefer $B$ over $C$. This works as expected under normal conditions, however, if the A--B link fails, then suddenly $D$ has made the wrong decision by preferring $E$. Traffic will now follow the
$A \cdot C \cdot D \cdot E \cdot G$ path, even though this path was not allowed by the policy. This is a violation of \emph{soundness}: The distributed implementation has used a route not specified by the policy. To make matters worse, the second preference $A \cdot C \cdot D \cdot F \cdot G$ is available in the network but not being used. This is a violation of \emph{completeness}: A path for the best possible route available exists in the network but is not being used by the distributed implementation.
%
The soundness violation could be fixed by tagging and filtering route advertisements appropriately so that $C$ rejects routes that go through $E$, however the completeness violation cannot be fixed. In fact, this policy cannot be implemented in BGP in a way that is policy compliant under all failures since $D$ cannot safely choose between $E$ and $F$ without knowing whether the A--B link is available.

@@

The problem of determining local preferences for each router is closely reflected in the structure of the PGIR. In particular, whenever a given router appears in multiple shadow nodes in the PGIR, then the compiler must decide which shadow to prefer.
%
In our compilation example from Figure~\ref{fig:example-compilation}, the topology node $C$ can receive an advertisement from $E$ in shadow $(C,-,2)$ or it can receive an advertisement from its neighbor $D$ in shadow $(C,3,2)$.
%
The compiler's task is to determine a \emph{total ordering} of shadow nodes for each router in the topology, which reflects the relative preference of advertisements received in each shadow. For example, if the compiler determines that, for router $C$, shadow $(C,3,2)$ can be locally preferred to shadow $(C,-,2)$, written as $(C,3,2) \leq_{lp} (C,-,2)$, then this means that $C$ will prefer advertisements heard from $D$ (with tag $(2,2)$) over $E$ (with tag $(-,2)$). Section~\ref{sec:abgp} discusses our encoding of preferences and filters in more detail.

@@

As shown in \S\ref{sec:motivation}, BGP aggregation can lead to subtle black-holing of traffic when failures occur. Determining when this can happen requires knowledge, not only of the topology, but also of the routing policy. For instance, a policy might require all traffic for a particular prefix to go over a single link before being aggregated, even when there are several available in the toplogy. If that one link fails, a black hole might be introduced.
%
Because the PGIR encodes the complete user policy and topology,  \sysname can efficiently check that aggregates do not black hole traffic for up to $k$ failures.

We frame the aggregation problem as a variant of the min-cut problem in the PGIR. Specifically, for each prefix that falls under an aggregate, we are interested in finding a lower bound on the number of failures required to disconnect the prefix's origin from its aggregation point. The difficulty, however, is that links in the topology can appear in multiple places in the PGIR, thus preventing the direct application of a standard min-cut algorithm.
%

Instead, we adopt the following simple strategy: $i)$ pick a random origin-to-aggregation path in the PGIR, $ii)$ remove all similar edges in the PGIR for the topological edges chosen, and $iii)$ repeat until no such path exists.
Because each path chosen is both policy compliant and edge disjoint (due to ii), the number of paths that we are able to remove lower bounds the number of failures required to disconnect the prefix from its aggregate, subject to the policy constraints.

For example, recall the datacenter example from \S\ref{sec:motivation}, with the policy
\CD{PG1} \Path \text{ }\End(\CD{A}), where \CD{PG1} falls under the \CD{PG} aggregate. Figure~\ref{fig:aggregation-safety} shows the simplified PGIR. Since the compiler knows aggregation will occur at $X$, and it knows that the \CD{PG1} prefix will originate at $A$, we can compute the number of failures it would take to disconnect $A$ from $X$. We could remove the $A$--$D$--$X$ path first. We would then need to remove any other $A$--$D$ or $D$--$X$ links from the PGIR (in this case none). Next, we could remove the links along the $A$--$C$--$X$ path, repeating the process. Because $A$ is then disconnected from $X$, the compiler knowns that 2 is a lower bound on the number of failures required to potentially introduce an aggreagation black hole for prefix \CD{PG1}. This process is repeated for other aggregation locations (e.g., $Y$).

@@

\section*{Acknowledgements}
